### 2020-10-30 README.Rmd
More tweaks to make duckdb work

```{r message = FALSE, warning = FALSE, error = FALSE, include = FALSE}
options(width = 120)
knitr::opts_chunk$set(cache = TRUE)
citesdb::cites_disconnect()
duckdb::duckdb_shutdown()
```

@@

The back-end database, [MonetDB](https://monetdb.org), is very fast and powerful, making analyses on such large data quite snappy using normal desktops and laptops. Here's the timing of the above query, which processes over 20 million records:

>>>>

```{r message = FALSE, warning = FALSE, error = FALSE, include = FALSE}
options(width = 120)
knitr::opts_chunk$set(cache = TRUE)
citesdb::cites_disconnect()
```

@@

The back-end database, [duckdb](https://duckdb.org/), is very fast and powerful, making analyses on such large data quite snappy using normal desktops and laptops. Here's the timing of the above query, which processes over 20 million records:
